---
title: "Writing Reports with R Markdown"
author: "Soojung Lee"
date: "2023-03-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=FALSE}
library(tidyverse)
```

This report was prepared to the attention of the United Nations. It analyzes the relationship between a country's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country's economic strength or weakness may be related to its public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions increase with a country's GDP. 

```{r data, include=FALSE}
gapminder_1997 <- read_csv("data/gapminder_1997.csv")
```

```{r gdp_lifeexp_1997, echo=FALSE}
ggplot(data = gapminder_1997) + 
  aes(x = gdpPercap, y = lifeExp, color = continent, size = pop/1000000) +
  geom_point() + 
  labs(x = "GDP Per Capita",
       y = "Life Expectancy",
       title = "Do people in wealthy countries live longer?",
       size = "Population (in millions)",
       color = "Continent")
```


```{r variables, include=FALSE}
nCountries <- gapminder_1997 %>% 
  select(country) %>% 
  n_distinct()

minGDP <- gapminder_1997 %>% 
  summarise(round(min(gdpPercap))) %>% 
  pull()

maxGDP <- gapminder_1997 %>% 
  summarise(round(max(gdpPercap))) %>% 
  pull()

```

The above plot shows the relationship between GDP per capita and life expectancy for a total of `r nCountries` countries. For this set of countries, economic wealth ranged from a minimum of USD `r minGDP` to a maximum of USD `r maxGDP` per capita. 

|Summary of Data|
|--------|--------|
|Number of Countries|`r nCountries`|
|Minimum GDP per capita|`r minGDP`|
|Maximum GDP per capita|`r maxGDP`|

```{r kabletable}
library(knitr)

gapminder_1997 %>% 
  filter(continent == "Oceania") %>% 
  kable()

```


# Header1 

## Header 2 

### My third header 


Exercise: R Markdown Syntax
* Create a bullet point list with three items
* as the first item, write the name of your currently favorite programming language in bold
* as the second item, write the name of a function you have so far found most useful in italics
* as the third item, write one thing you want to learn next on your programming journey in bold italics
* turn your bullet point list into a numbered list
* create a fourth list item and find an online guide and/or cheat sheet for basic Markdown syntax, write its name down and hyperlink its url 



My list:
- **R**
- *mutate()*
- ***python***

1. **R**
2. *mutate()*
3. ***python***
4. [https://www.markdownguide.org/cheat-sheet/](This is a link for a cheat sheet for basic Markdown syntax)


Steps for a git flow:

*** git pull (before commiting changes)

1. git status 
2. git add 
3. git commit -m "message"
4. git push 

This is my final report. 








